---
title: true
geometry: margin=2.25cm
header-includes:
  - \usepackage{../ve414}
  - \author{\href{mailto:liuyh615@sjtu.edu.cn}{Yihao Liu} (515370910207)}
  - \semester{Summer}
  - \year{2019}
  - \subtitle{Assignment}
  - \subtitlenumber{3}
  - \blockinfo{}
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question1

### (a)

The joint likelihood is 
$$f_{\mathbf{X}\mid\{\mathbf{Y},\alpha,\beta\}}=\prod_{i=1}^n\text{Poisson}(x_i;y_i)=\prod_{i=1}^n\frac{y_i^{x_i}e^{-y_i}}{x_i!}.$$

The conditional prior is
$$f_{\mathbf{Y}\mid\{\alpha,\beta\}}=\prod_{i=1}^n\text{Gamma}(y_i;\alpha,\beta)=\prod_{i=1}^n\frac{\beta^\alpha y_i^{\alpha-1}e^{-\beta y_i}}{\Gamma(\alpha)}.$$

The hyperprior is
$$f_{\alpha,\beta}=\text{Exp}(\alpha;a)\cdot\text{Gamma}(\beta;b,c)=ae^{-a\alpha}\cdot\frac{c^b\beta^{b-1}e^{-c\beta}}{\Gamma(b)}\propto \beta^{b-1}e^{-a\alpha-c\beta}.$$

The joint posterior is
$$f_{\{\mathbf{Y},\alpha,\beta\}\mid\mathbf{X}}\propto f_{\mathbf{X}\mid\{\mathbf{Y},\alpha,\beta\}}\cdot f_{\mathbf{Y}\mid\{\alpha,\beta\}} \cdot f_{\alpha,\beta}\propto \beta^{b-1}e^{-a\alpha-c\beta}\prod_{i=1}^n\frac{\beta^\alpha y_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}}{\Gamma(\alpha)}=\frac{\beta^{n\alpha+b-1}e^{-a\alpha-c\beta}}{\Gamma(\alpha)^n}\prod_{i=1}^ny_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}.$$

### (b)

$X_1, X_2, \cdots, X_n, \alpha, \beta$ should be independent with each other.

$Y_1, Y_2, \cdots, Y_n, \alpha, \beta$ should be independent with each other.

$\{X_i, Y_j\mid i\neq j\}$ should be independent.


### (c)

The conditional posterior $f_{\{\mathbf{Y},\beta\}\mid\{\mathbf{X},\alpha\}}$ is
$$f_{\{\mathbf{Y},\beta\}\mid\{\mathbf{X},\alpha\}}=\frac{f_{\{\mathbf{Y},\alpha,\beta\}\mid\textbf{X}}}{f_{\alpha\mid\mathbf{X}}}\propto f_{\{\mathbf{Y},\alpha,\beta\}\mid\textbf{X}}=\frac{\beta^{n\alpha+b-1}e^{-a\alpha-c\beta}}{\Gamma(\alpha)^n}\prod_{i=1}^ny_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}\propto \beta^{n\alpha+b-1}e^{-c\beta}\prod_{i=1}^ny_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}.$$

We have
$$y_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}\propto\text{Gamma}(yi;x_i+\alpha,\beta+1)=\frac{(\beta+1)^{x_i+\alpha}}{\Gamma(x_i+\alpha)}y_i^{x_i+\alpha-1}e^{-(\beta+1)y_i},$$
$$\beta^{n\alpha+b-1}e^{-c\beta}\propto\text{Gamma}(\beta;n\alpha+b,c)=\frac{c^{n\alpha+b}}{\Gamma(n\alpha+b)}\beta^{n\alpha+b-1}e^{-c\beta}.$$

So the normalized conditional posterior $f_{\{\mathbf{Y},\beta\}\mid\{\mathbf{X},\alpha\}}$ is
$$f_{\{\mathbf{Y},\beta\}\mid\{\mathbf{X},\alpha\}}=\frac{c^{n\alpha+b}}{\Gamma(n\alpha+b)}\beta^{n\alpha+b-1}e^{-c\beta}\prod_{i=1}^n\frac{(\beta+1)^{x_i+\alpha}}{\Gamma(x_i+\alpha)}y_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}.$$

### (d)

The conditional posterior $f_{\mathbf{Y}\mid\{\mathbf{X},\alpha,\beta\}}$ is
$$f_{\mathbf{Y}\mid\{\mathbf{X},\alpha,\beta\}}=\frac{f_{\{\mathbf{Y},\alpha,\beta\}\mid\textbf{X}}}{f_{\{\alpha,\beta\}\mid\mathbf{X}}}\propto \beta^{n\alpha+b-1}e^{-c\beta}\prod_{i=1}^ny_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}\propto\prod_{i=1}^ny_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}.$$

Similar to (c), the normalized conditional posterior $f_{\mathbf{Y}\mid\{\mathbf{X},\alpha,\beta\}}$ is
$$f_{\mathbf{Y}\mid\{\mathbf{X},\alpha,\beta\}}=\prod_{i=1}^n\frac{(\beta+1)^{x_i+\alpha}}{\Gamma(x_i+\alpha)}y_i^{x_i+\alpha-1}e^{-(\beta+1)y_i}.$$

The marginal posterior is
$$f_{\{\alpha,\beta\}\mid\mathbf{X}}=\frac{f_{\{\mathbf{Y},\alpha,\beta\}\mid\mathbf{X}}}{f_{\mathbf{Y}\mid\{\mathbf{X},\alpha,\beta\}}}\propto \frac{\beta^{n\alpha+b-1}e^{-a\alpha-c\beta}}{\Gamma(\alpha)^n}\prod_{i=1}^n\frac{\Gamma(x_i+\alpha)}{(\beta+1)^{x_i+\alpha}}=\beta^{n\alpha+b-1}e^{-a\alpha-c\beta}\prod_{i=1}^n\frac{\Gamma(x_i+\alpha)}{\Gamma(\alpha)(\beta+1)^{x_i+\alpha}}.$$

## Question2

### (a)

Let 
$$z=\left\{\begin{aligned}0, &\quad\text{a greasy grouper}\\1, &\quad\text{a tiger grouper}\end{aligned}\right..$$

Then $$C(y,z)=\left\{\begin{aligned}0.1, &\quad y=0,z=1\\0.9, &\quad y=1,z=0\\0, &\quad y=z\end{aligned}\right..$$


And since there are twice as many tiger groupers in the tank,
$$f_{Y=0}=\frac{1}{3},\quad f_{Y=1}=\frac{2}{3}.$$

So
$$\begin{aligned}f_{Y=0\mid\mathbf{X}}&\propto f_{\mathbf{X}\mid Y=0}\cdot f_{Y=0}\\&=\frac{1}{3}f_{\mathbf{X}\mid Y=0}\\&=\frac{1}{3}(2\pi)^{-1}(\det\mathbf{\Sigma_g})^{-1/2}\exp\left[-\frac{1}{2}(\mathbf{x}-\mu_g)^T\mathbf{\Sigma_g^{-1}}(\mathbf{x}-\mu_g)\right]\\&=\frac{1}{6\sqrt{3}\pi}\exp\left[\frac{1}{3}(-139-x_1^2+7x_2+16x_1+x_1x_2-x_2^2)\right],\end{aligned}$$
$$\begin{aligned}f_{Y=1\mid\mathbf{X}}&\propto f_{\mathbf{X}\mid Y=1}\cdot f_{Y=1}\\&=\frac{2}{3}f_{\mathbf{X}\mid Y=1}\\&=\frac{2}{3}(2\pi)^{-1}(\det\mathbf{\Sigma_t})^{-1/2}\exp\left[-\frac{1}{2}(\mathbf{x}-\mu_t)^T\mathbf{\Sigma_t^{-1}}(\mathbf{x}-\mu_t)\right]\\&=\frac{1}{3\sqrt{23}\pi}\exp\left[\frac{1}{23}(-207-x_1^2+69x_2+x_1x_2-6x_2^2)\right].\end{aligned}$$
The optimal decision rule is
$$\begin{aligned}z=\delta(\mathbf{x})&=\mathop{\arg\min}_{z\in S}\sum_{y\in S}C(y,z)f_{Y=y\mid\mathbf{X}}\\&=\mathop{\arg\min}_{z\in S}\left\{0.1z\cdot f_{Y=0\mid\mathbf{X}}+0.9(z-1)\cdot f_{Y=1\mid\mathbf{X}}\right\}\\&=\mathop{\arg\min}_{z\in S}\left\{0.1z\cdot \frac{1}{6\sqrt{3}\pi}\exp\left[\frac{1}{3}(-139-x_1^2+7x_2+16x_1+x_1x_2-x_2^2)\right]+\right.\\&\qquad\qquad\quad\left. 0.9(z-1)\cdot \frac{1}{3\sqrt{23}\pi}\exp\left[\frac{1}{23}(-207-x_1^2+69x_2+x_1x_2-6x_2^2)\right]\right\}\end{aligned}$$

### (b)

Let 
$$f(\mathbf{x})=0.1\cdot f_{Y=0\mid\mathbf{X}}-0.9\cdot f_{Y=1\mid\mathbf{X}},$$ 
then when $f(\mathbf{x})>0$, it should be greasy grouper; when $f(\mathbf{x})<0$, it should be tiger grouper. We can have a contour plot of $f(\mathbf{x})$ so that the decision boundary is the contour $f(\mathbf{x})=0$.

```{r ex2.2, fig.height=7, fig.width=7, fig.align='center'}
greasy <- function(x, y) {
    0.1 / (6 * sqrt(3) * pi) * exp((-139-x^2+7*y+16*x+x*y-y^2) / 3)
}
tiger <- function(x, y) {
    0.9 / (3 * sqrt(23) * pi) * exp((-207-x^2+69*y+x*y-6*y^2) / 23)
}
difffunc <- function(x, y) {
    greasy(x,y) - tiger(x,y)
}
x <- y <- seq(0, 20, length= 200)
z <- outer(x, y, difffunc)
contour(x, y, z)
```

### (c)

I will classify the fish as a greasy grouper in the top-right corner in the figure because the contour is rising in the region so that $f(\mathbf{x})>0$. In other region, I will classify the fish as a tiger grouper.







